---
title: "Worst Plots Contest"
output:
        github_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(dplyr)
library(ggplot2)
knitr::opts_knit$set(root.dir = "C:/Users/piyus/Downloads/ISQA8600/Data Cleaning Document")
```

### Loading Data

```{r}
MyData <- read.csv("HFS Service Data.csv", na.strings = "")
```

## Plot No. 1

```{r}
library(ggplot2)
ggplot(MyData, aes(x =program_name , y=duration, color=program_name))+stat_summary(fun = "mean", geom = "bar")
```

1. This plot is bad because there are too many points in y-axis which makes it miserable. The relationship between x axis and y axis is vague and does not have any useful interpretation about the data. We can't make any decisions out of this plot.

## Plot No. 2

```{r}

general_location_group <- MyData %>% group_by(general_location) %>% count(sort=TRUE)
ggplot(general_location_group) + geom_point(mapping = aes(x =general_location, y = n)) +
  labs(title = "Number of Records per Location", y = "Number of Records", x = "general_location")
```

1. This plot has a meaningful plotting with respect to record count per general location. But the representational error for y-axis label is what makes this plot bad.
2. The points are also not in ordered form, which makes it difficult to find the highest and lowest value by looking at the plot.
